\documentclass[12pt, draft]{article}
\usepackage[margin= 0.75in]{geometry}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{mathabx}
\usepackage{ulem}
\usepackage{enumerate}
\usepackage{float}
\usepackage{graphicx}
\usepackage{color}
\usepackage{subfigure}

\begin{document}

\newtheorem{prop}{Proposition}

\title{Think of a title later}
\author{Ansel Blumers and Ankan Ganguly}
\maketitle

\begin{abstract}
Abstract goes here.
\end{abstract}

\newpage

\tableofcontents

\newpage

\section{Introduction}

Write an introduction here.

\section{Methods}

In this paper, we used the simulated Integrate and Burst model introduced in \cite{Fiete}.

\subsection{Integrate and Burst Model}

Equations and paper reference here.

\subsection{Learning}

Introduction to what we did.

\subsubsection{STDP Learning}

Talk about STDP learning in this implementation.

\subsubsection{Hebbian Learning}

Talk about Hebbian learning here.

\subsection{Parameter Choices}

Talk about how we chose parameters here.

\section{Results}

Introduce the big idea and what we got.

\subsection{Parameter Tuning}

\begin{itemize}
\item 4000 Hz doesn't work! (Burst Plot)

\item Mention annealing and our choice of \(r_{in}, \eta\) and \(\epsilon\). Name the two data sets we refer to for the remainder of the paper. (Scatter Error Function)

\item Setting \(w_{max}\). (Burst History)
\end{itemize}

\subsection{Convergence and Stability}

\begin{itemize}
\item Demonstrate the stability of our IB model by showing the firing rate plot and how it splits according to \(r_{in}\).

\item Plot Weight and \(WW^T\) for 4000 and 6000 Hz to show some level of convergence.

\item Plot error function over time from normal and from permutation matrix

\item Describe why the error function converges away from 0.
\end{itemize}

\subsection{Hebbian Learning versus STDP}

\begin{itemize}
\item Introduce the idea of the refutation. 
\item Give a theoretical description why the type of learning should be relatively unimportant.
\item Compare plots (\(WW^T\), Error vs Time, Burst History).
\end{itemize}

\section{Discussion}

Further improvements that could be made to our model and where this research could be taken.

\section{Summary}

Quick summary of our results and everything.



\bibliographystyle{plain}
\bibliography{Songbird_paper}

\end{document}